A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 textos/dsrt/engaoi.tex
eng

\section{Conclusion}
\label{conclusion}
In this work, we presented the \malg\ interest management algorithm, whose main idea is to adapt the state update frequency of the game entities according to their relevance to each client that will receive the updates. The \malg\ area of interest shape consists of a circular sector, corresponding to the player field of view, plus a smaller circle, which represents the area close to that player's avatar. The goal of this close area is to maintain the game state inside it the most updated possible, in order to improve the game near the avatar. Joining these characteristics, we obtained an algorithm that achieved a significant reduction of the maximum upload bandwidth utilization by the server, which decreased 52.03\% and 33.10\%, compared to circle and field of view based interest management algorithms, respectively. The average upload bandwidth utilization by the server also decreased 63.51\% and 33.58\%, compared to the same algorithms.

>>>>

\section{Conclusion}
\label{conclusion}
In this work, we presented the \malg\ interest management algorithm, whose main idea is to adapt the state update frequency of the game entities according to their relevance to each client that will receive the updates. The \malg\ area of interest consists of a circular sector, corresponding to the player field of view, plus a smaller circle, which represents the area close to that player's avatar. The goal of this close area is to maintain the game state inside it the most up-to-date possible, in order to improve the game near the avatar. Joining these characteristics, we obtained an algorithm that achieved a significant reduction of the maximum upload bandwidth utilization by the server, which decreased 52.03\% and 33.10\%, compared to circle and field of view based interest management algorithms, respectively. The average upload bandwidth utilization by the server also decreased 63.51\% and 33.58\%, compared to the same algorithms.
